Fractional anisotropy as a tracer of cosmic voids

### 2014-11-23 cosmic_voids.tex
New figures changing radial bins in order to have a more significant statistics per bin

%.........................................................................
%FIGURE 6: Density profile of voids for each defined scheme
\begin{flushleft}
\begin{figure*}
\centering
  \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
  width=0.3\textheight]{./figures/voids_density_TwebFAG.pdf}
  \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
  width=0.3\textheight]{./figures/voids_density_VwebFAG.pdf}
%  \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
%  width=0.24\textheight]{./figures/voids_density_TwebDLG.pdf}

  \

  \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
  width=0.3\textheight]{./figures/voids_velocity_TwebFAG.pdf}
  \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
  width=0.3\textheight]{./figures/voids_velocity_VwebFAG.pdf}
%  \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
%  width=0.24\textheight]{./figures/voids_velocity_TwebDLG.pdf}

  \captionof{figure}{\small Density and velocity profiles of voids for 
  each finding scheme.}

>>>>

%.........................................................................
%FIGURE 6: Density profile of voids for each defined scheme
\begin{flushleft}
\begin{figure*}
\centering
  \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
  width=0.25\textheight]{./figures/voids_density_TwebFAG0.pdf}
  \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
  width=0.25\textheight]{./figures/voids_density_VwebFAG0.pdf}
  \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
  width=0.25\textheight]{./figures/voids_density_TwebFAG1.pdf}
  \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
  width=0.25\textheight]{./figures/voids_density_VwebFAG1.pdf}

  \captionof{figure}{\small Density of voids for each finding scheme.}

%.........................................................................
%FIGURE 7: Velocity profile of voids for each defined scheme
\begin{flushleft}
\begin{figure*}
\centering
  \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
  width=0.25\textheight]{./figures/voids_velocity_TwebFAG0.pdf}
  \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
  width=0.25\textheight]{./figures/voids_velocity_VwebFAG0.pdf}
  \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
  width=0.25\textheight]{./figures/voids_velocity_TwebFAG1.pdf}
  \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
  width=0.25\textheight]{./figures/voids_velocity_VwebFAG1.pdf}

  \captionof{figure}{\small Velocity of voids for each finding scheme.}
